A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-01-29 paper.tex
Redid change
minor

An abstraction of the game restricts actions available to one of the players.
Specifically, we consider abstractions represented as trees of actions,
referred to as \emph{abstract game trees}.  Figure~\ref{fig:agt} shows an
example abstract game tree for the controller (abstract game trees for the
environment are similar).  In the abstract game, the controller is required to
pick actions from the tree, starting from the root node.  After reaching a
leaf, it continues playing unrestricted.  The tree in Figure~\ref{fig:agt}
restricts the initial controller action to the set $\{a, d\}$.  After choosing
action $a$, the controller is required to play action $b$ in the next round.
It then reaches a leaf of the tree and continues playing unrestricted.  The
root of the tree is annotated by the initial state $s$ of the abstract game and
the bound $k$ on the number of rounds.  We denote $\textsc{nodes}(T)$ the set
of all nodes of a tree $T$, $\textsc{leaves}(T)$ the subset of leaf nodes, for
edge $e$ $\textsc{action}(e)$ is the action that labels the edge, and for node
$n$ $\textsc{height}(n)$ as the maximal distance from n to a leaf. For a node
$n$ of the tree, $\textsc{succ}(n)$ is the set of pairs $\langle e, n' \rangle$
where $n'$ is a child node of $n$ and $e$ is the edge connecting $n$ and $n'$.

@@

        \caption{Extended AGT}

@@

    \caption{Abstract game trees}

>>>>

An abstraction of the game restricts actions available to one of the players.
Specifically, we consider abstractions represented as trees of actions,
referred to as \emph{abstract game trees}.  Figure~\ref{fig:agt} shows an
example abstract game tree for the controller (abstract game trees for the
environment are similar).  In the abstract game, the controller is required to
pick actions from the tree, starting from the root node.  After reaching a
leaf, it continues playing unrestricted.  The tree in Figure~\ref{fig:agt}
restricts the initial controller action to the set $\{a, d\}$.  After choosing
action $a$, the controller is required to play action $b$ in the next round.
It then reaches a leaf of the tree and continues playing unrestricted.  The
root of the tree is annotated by the initial state $s$ of the abstract game and
the bound $k$ on the number of rounds.  We denote $\textsc{nodes}(T)$ the set
of all nodes of a tree $T$, $\textsc{leaves}(T)$ the subset of leaf nodes.  For
edge $e$, $\textsc{action}(e)$ is the action that labels the edge, and for node
$n$, $\textsc{height}(n)$ is the maximal distance from n to a leaf. For node
$n$ of the tree, $\textsc{succ}(n)$ is the set of pairs $\langle e, n' \rangle$
where $n'$ is a child node of $n$ and $e$ is the edge connecting $n$ and $n'$.

@@

        \caption{AGT extended to bound 3 with arbitrary controller actions}

@@

    \caption{Abstract game trees.}
